QPLIB: A Library of Quadratic Programming Instances

### 2017-01-20 QPLIB-2.3.tex
knitro has an active set solver and multistart for nlps

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are {\sc ConOpt}, {\sc IpOpt}, {\sc Minos}, {\sc SnOpt} and {\sc KNitro}\todo{check capitalization of solver names}. The methods are local search algorithms and are essentially of the following types: %Note that traditionally {\sc KNitro} used to be a local (nonconvex) NLP solver.
%All of these solvers implement essentially three types of local search methods for continuous NLPs:
\todo{sequential linear programming, sequential quadratic programming, trust-region}
\begin{itemize}
 \item active set methods ({\sc ConOpt}, {\sc Minos}, {\sc SnOpt}) \cite{Dost09};
 %
 \item interior point methods ({\sc IpOpt}, {\sc KNitro}) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize} \todo{doesn't Knitro additionally implement an active set or SQP algorithm?}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are {\sc oqnlp}, {\sc msnlp} and certain sub-solvers of {\sc lgo}. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search ({\sc lgo\_gars});
 %
 \item multi-start ({\sc lgo\_ms}, {\sc msnlp}, {\sc oqnlp}); specifically, the former two apply to QCQ whereas the latter to QGQ.
\end{itemize}

>>>>

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are {\sc ConOpt}, {\sc IpOpt}, {\sc Minos}, {\sc SnOpt} and {\sc KNitro}\todo{check capitalization of solver names}. The methods are local search algorithms and are essentially of the following types: %Note that traditionally {\sc KNitro} used to be a local (nonconvex) NLP solver.
%All of these solvers implement essentially three types of local search methods for continuous NLPs:
\todo{sequential linear programming, sequential quadratic programming, trust-region}
\begin{itemize}
 \item active set methods ({\sc ConOpt}, {\sc Minos}, {\sc SnOpt}, {\sc KNitro}) \cite{Dost09};
 %
 \item interior point methods ({\sc IpOpt}, {\sc KNitro}) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are {\sc oqnlp}, {\sc msnlp}, {\sc knitro}, and certain sub-solvers of {\sc lgo}. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search ({\sc lgo\_gars});
 %
 \item multi-start ({\sc knitro}, {\sc lgo\_ms}, {\sc msnlp}, {\sc oqnlp}); specifically, the former three apply to QCQ whereas the latter to QGQ.
\end{itemize}
